Hierarchical ARIMA

### 2020-08-18 KB_modeling.Rmd
nothing

dat %>%
  filter(team == "San Diego Padres") %>%
  ggplot() + 
  geom_line(aes(x = date, y = qn_ghits), color = "deeppink") +
  geom_line(aes(x = date, y = lump_preds), color = "cornflowerblue")
```
This is much better.

>>>>

dat %>%
  filter(team == "San Diego Padres") %>%
  ggplot() + 
  geom_line(aes(x = date, y = qn_ghits), color = "deeppink") +
  geom_line(aes(x = date, y = lump_preds), color = "cornflowerblue")
```

This is much better.
